Dataset-level report

### 2019-11-14 analysis/reports/dat_report_template.Rmd
This template should work with BBS, FIA if that becomes problematic

loadd(all_di, cache = cache)

>>>>

if("all_di" %in% cached(cache = cache)) {
loadd(all_di, cache = cache)
} else {
  all_di_names <- cached(cache = cache)[ which(grepl(cached(cache = cache), pattern = "all_di_s_"))]
  all_di_list <- lapply(all_di_names, FUN = readd, cache = cache, character_only =T)
  names(all_di_list) <- all_di_names
  all_di <- bind_rows(all_di_list)
  rm(all_di_names)
  rm(all_di_list)
}
